Damage localization based on vibrations

### 2016-12-06 rapport/paper.tex
paper ended

\subsection{Result}

For the simulation, we put a sensor on each mass.

Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF (absolute value) of one sensor (ten in total), against frequencies. We can see three peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak. Seeing this curve for each sensor, we observed that certain sensors have one peak for each natural frequencies, and others sensors have one peak for each except one, relied on the position of the sensor in the system. It is problematic because it is around the natural frequencies of the system that we have better datas, but if certain sensors haven't response with certain frequencies, we could miss out on a damage.

@@

Figure (\ref{damage}) is the FRF values for ten sensors (at a fixed frequency). Here, we easily can see that there is a damage between the sensors 4 and 5 (as we noticed it in the simulation). However,

@@

Figure (\ref{damage2}) is the FRF values for the same ten sensors that in Figure (\ref{damage}), at a different frequency.

@@

Finaly, we can see in Figure (\ref{globalerror}) the global error described in section IV.

@@

>>>>

\subsection{Results}

For the following simulation results, we consider a system with 10 masses. We put a sensor on each mass. For the damaged state, we lower the stifness of the spring between sensors 4 and 5 by 90\%. The values of the FRF on the figures are the norm of the FRF values.

Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF of one sensor, against frequencies. We can see three peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak. Seeing this curve for each sensor, we observed that certain sensors have one peak for each natural frequencies, and others sensors have one peak for each except one, relied on the position of the sensor in the system. It is problematic because it is around the natural frequencies of the system that we have better datas, but if certain sensors haven't response with certain frequencies, we could miss out on a damage.

@@

@@

Figure (\ref{damage}) is the FRF values for the ten sensors (at a fixed frequency). Here, we easily can see that there is a damage between the sensors 4 and 5 (as we noticed it). However, as the damaged FRF is away from the reference FRF, we can see that there isn't a significant loss of regularity at sensors 4 and 5 (the interpolation error isn't high).

Figure (\ref{damage2}) is the FRF values for the same ten sensors that in Figure (\ref{damage}), with the same damage, at a different frequency. Here, we can see a significant loss of regularity at sensors 6 and 8. It shows that we have to select the frequencies where we calculate the interpolation error. Indeed, an hypothesis is that significant values of the FRF are near to the natural frequencies of the system (that we can see in Figure (\ref{frf_freq})).

@@

Finaly, we can see in Figure (\ref{globalerror}) the global error described in section IV. The two first and last values (i.e. for sensor 0,1,8 and 9) aren't useful because cubic spline interpolation requires two values on each side of the interpolate value. We can see that, if we consider all frequencies for the error calcul, results aren't as we want: here the damaged system has a FRF more regular than the undamaged system. A selection of the frequencies is necessary.

@@

In this paper, we presented the structure heatlh monitoring and a state of the art for this. Then we detailled one of the methods, the FRF interpolation method, and some physical models. Last, we presented our simulation with a sping-mass system and our results with the implementation of the FRF interpolation method.

We saw that we have to do a selection of the frequencies where we calculate the interpolation error.

In the second part of this project, we will do a detailled analysis of the statistical behaviour of the interpolation error.
